A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-04-13 ICLP Paper/samplepaper.tex
abstract

Scheduling methods are important for effective production and logistics management, where tasks need to be allocated and performed by limited resources.
In particular, the Job-shop Scheduling Problem (JSP) is a well-known and challenging
combinatorial optimization problem in which tasks sharing a machine are to be arranged
in sequence such that encompassing jobs can be completed as early as possible.
Given that already moderately sized JSP instances can turn out as highly combinatorial,
so that neither optimal schedules nor the runtime to termination of complete optimization methods
is known, efficient approaches to approximate good-quality schedules are of interest.
In this paper, we propose problem decomposition into time windows whose operations
can be successively scheduled and optimized by means of multi-shot ASP solving.
From a computational perspective, decomposition aims to split highly complex scheduling tasks into better manageable subproblems with a balanced number of 
operations, so that good-quality or even optimal partial solutions can be

@@

respect the precedence of operations within their jobs, and partial schedules

@@

in similar runtime on the full problem.

@@

into the iterative scheduling process in order to counteract limitations of window-wise optimization restricted to partial schedules.

@@

Effective scheduling methods are essential for complex manufacturing and logistics systems,
where allocating and performing diverse tasks within resource capacity limits 
is one of the most critical challenges for production management \citep{uzsoy2000performance}.

@@

which sequences of operations need to be processed by machines such that a given objective
like the makespan for completing all jobs or their tardiness w.r.t.\ deadlines is minimized.
Finding optimal JSP solutions, determined by a sequence of operations for each machine,
is an NP-hard combinatorial problem
\citep{garey1976complexity,lenstra1977complexity,liu2008prediction},
and optimal schedules as well as termination guarantees can be extremely challenging
or beyond reach 
of complete optimization methods already for moderately sized instances.
For example, it took about $20$ years to develop a search procedure able to find a
(provably) optimal solution for an instance called FT10 with $10$ jobs
\citep{adams1988shifting,zhang2010hybrid},
each consisting of a sequence of $10$ operations to be processed by $10$ machines.

>>>>

Scheduling methods are important for effective production and logistics management, where tasks need to be allocated and performed with limited resources.
In particular, the Job-shop Scheduling Problem (JSP) is a well-known and challenging combinatorial optimization problem in which tasks sharing a machine are to be arranged in a sequence such that encompassing jobs can be completed as early as possible.
% remove double 'so that'
Given that already moderately sized JSP instances can be highly combinatorial, and neither optimal schedules nor the runtime to termination of complete optimization methods is known, efficient approaches to approximate good-quality schedules are of interest.
In this paper, we propose problem decomposition into time windows whose operations can be successively scheduled and optimized by means of multi-shot ASP solving.
From a computational perspective, decomposition aims to split highly complex scheduling tasks into better manageable subproblems with a balanced number of  operations so that good-quality or even optimal partial solutions can be

@@

respect the precedence of operations within their jobs and partial schedules

@@

in similar runtime on the entire instance.

@@

into the iterative scheduling process to counteract window-wise optimization limitations restricted to partial schedules.

@@

Effective scheduling methods are essential for complex manufacturing and transportation systems, where allocating and performing diverse tasks within resource capacity limits is one of the most critical challenges for production management \citep{uzsoy2000performance}.

@@

which sequences of operations need to be processed by machines such that a given objective,
like the makespan for completing all jobs or their tardiness w.r.t.\ deadlines, is minimized.
Finding optimal JSP solutions, determined by a sequence of operations for each machine, is an NP-hard combinatorial problem \citep{garey1976complexity,lenstra1977complexity,liu2008prediction}. Therefore, optimal schedules and termination guarantees can be extremely challenging or even unreachable for complete optimization methods already for moderately sized instances.
For example, it took about $20$ years to develop a search procedure able to find a (provably) optimal solution for an instance called FT10 with $10$ jobs
\citep{adams1988shifting,zhang2010hybrid}, each consisting of a sequence of $10$ operations to be processed by $10$ machines.
